\section{External Dependencies}


Below are the results of learning how to import external libraries and Linux packages into the project. At the end of this section, I have included a table of candidate open source project that I will likely use for audio processing. 

\textbf{Note:} The table may change as I learn more while working on the project. I am even open to the idea of combining several open source packages if it is necessary.


\begin{itemize}
	\item NOTES:
	\begin{itemize}
		\item You can include C++ dependencies (libraries) in your project through clickable.
		\item From what I currently understand, Clickable can compile ARM software into desktop architecture as it uses a container. It may not be able to go the other way (x86 / x86\_64 -> ARM)
		\item Interestingly, it can run the app in a continuous integration environment due to the use of the ARM -> Desktop container. There are guides on how to do CLCI
		\item The consensus on Quora seems to be that the difficulty will range from: rebuilding with an ARM compiler to rewriting from scratch. It all depends on the type of software
	\end{itemize}
\end{itemize}



\begin{itemize}
	\item Links
	\begin{itemize}
		\item https://docs.ubports.com/en/latest/appdev/guides/dependencies.html
		\item https://ubports.com/blog/ubports-news-1/post/introduction-to-clickable-147
		\item https://clickable.bhdouglass.com/en/latest/
		\item https://www.quora.com/How-hard-is-it-to-port-an-application-from-x86-to-ARM
	\end{itemize}
\end{itemize}



\begin{itemize}
\item Contains the largest list of open source audio software that I could find. Look under "Software Development Libraries \& APIs":
	\begin{itemize}
	\item https://github.com/webprofusion/OpenAudio	
	\end{itemize}
\end{itemize}





\textbf{Audio Processing Libraries / Tools:}

%\begin{tabular}{|l|l|l|l|l|l|l|}
\begin{tabular}{|p{2.25cm}|p{2.25cm}|p{2.25cm}|p{2.25cm}|p{2.25cm}|p{2.25cm}|p{2.25cm}|}
\hline
\thead{Name} & \thead{Brief Description} & \thead{License Type} & \thead{ARM Build} & \thead{C++ library} & \thead{Estimated work} & \thead{Link} \\ 
                    \hline
Faust & 
Functional programming language for real-time signal processing & 
GNU General Public License v2.0 & 
Y, doesn't depend on external libraries so compile the generated code into ARM & 
Y, after generating the code & 
May require knowing the full extent of code functionality. That may hamper scalability, and create software design compromises. However, there is a JIT compiler that may help with this. & 
https://faust.grame.fr/ \\    \hline

RustAudio & 
Collection of audio processing and plugin libraries for the Rust language & 
MIT and Apache, to name a few & 
Not sure, may depend on how much of the code is native Rust & 
N, but it is written in Rust & 
This is a collection of REPO's. I think cpal and dsp-chain will take care of most of the use-cases, without too much effort. Unless this can't compile for ARM ( or is too slow), I might consider this a top pick, pretty straightforward. & 
https://github.com/RustAudio \\    \hline

DISTRHO  & 
C++ framework for creating cross-platform audio plugins. DPF can build for LADSPA, DSSI, LV2, and VST formats. & 
ISC License & 
Most likely, seems to be mostly native code & 
Y & 
Might be a lot, doesn't hold your hand & 
https://github.com/DISTRHO/DPF \\    \hline


JUCE & 
Cross-platform C++ framework for developing desktop and mobile apps and audio plugins & 
\small{https://juce.com/get-juce} & 
Not natively. There are threads for workarounds. Also, most users of this software are for Windows / Mac Desktop users. & 
Y & 
The library itself seems straightforward, but lack of Linux ARM compatibility might add extra work. & 
\small{https://juce.com/learn/tutorials}  \\    \hline



\end{tabular}



\begin{itemize}
\item TODO: Alternatively, review this link to see if creating these effects from scratch is feasible: 
	\begin{itemize}
		\item https://lisyarus.github.io/blog/programming/2022/10/15/audio-mixing.html
	\end{itemize}
\end{itemize}


